$\pi$SOD-M: A Methodology for Building Service-Oriented Applications in the Presence of Non-Functional Properties

### 2014-03-09 JournalToSubmit2013/intro.tex
Introduction changed 10.04.2014

 This paper describes the methodology $\pi$-SODM based on  an NFP model including a set of concepts  for  modeling  NFP in service-oriented applications.
Accordingly, the remainder of the paper is organized as follows.
Section\ref{sec:relworks} summarizes the general principles of existing works for addressing NFP and associating them to service compositions. Section \ref{sec:motivation} introduces the meta-models of the $\pi$-SODM and transformation rules. Section \ref{sec:implementation} describes the $\pi$-SODM environment that provides tools for building service based applications according to the $\pi$-SODM methodology. Section\ref{sec:flyingPig} describes the experiment that we conducted for validating our methodology and discusses lessons learned. Finally, Section \ref{sec:conclusions} concludes the paper and gives research perspectives.

>>>>

 This paper describes the methodology $\pi$-SODM based on  an NFP model including a set of concepts  for  modeling  NFP in service-oriented applications.
Accordingly, the remainder of the paper is organized as follows.
Section\ref{sec:relworks} summarizes the general principles of existing works for addressing NFP and associating them to service compositions. Sections \ref{sec:motivation}  and \ref{sec:mmrules} introduce respectively the meta-models of the $\pi$-SODM and transformation rules. Section \ref{sec:implementation} describes the $\pi$-SODM environment that provides tools for building service based applications according to the $\pi$-SODM methodology. Section \ref{sec:flyingPig} describes the experiment that we conducted for validating our methodology and discusses lessons learned. Finally, Section \ref{sec:conclusions} concludes the paper and gives research perspectives.
